\documentclass[a5paper, parskip=half, DIV=17]{scrartcl}
\usepackage{hexman}

\RedeclareSectionCommand[
  runin=false,
  beforeskip=2.0\baselineskip,
  afterskip=-0.0\baselineskip
]{section}

\usepackage{fontspec}
\setmainfont{Tex Gyre Schola}

\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{epsdice}

\pagestyle{empty}
\raggedright
\begin{document}
\section*{Ghost Selection}
Each round, two of the four ghosts will move. To determine which ghosts will move, roll the die and consult the following table:

\begin{center}
\begin{tabular}{c l l}\toprule
Die & Ghost 1 & Ghost 2 \\\midrule
\raisebox{-0.125ex}{\epsdice{1}} & Alice (red) & Bob (yellow) \\
\raisebox{-0.125ex}{\epsdice{2}} & Alice (red) & Clyde (green) \\
\raisebox{-0.125ex}{\epsdice{3}} & Alice (red) & Daryl (blue) \\
\raisebox{-0.125ex}{\epsdice{4}} & Bob (yellow) & Clyde (green) \\
\raisebox{-0.125ex}{\epsdice{5}} & Bob (yellow) & Daryl (blue) \\
\raisebox{-0.125ex}{\epsdice{6}} & Clyde (green) & Daryl (blue) \\\bottomrule
\end{tabular}
\end{center}

\section*{Ghost Movement}
The movement rules for the ghosts are:
\begin{itemize}[leftmargin=*]
	\item If a ghost is at the same flower as the player, then they take one step towards the player via the shortest route. In the case of a tie, the ghost steps in the clockwise direction.
	\item If a ghost is at a different flower than the player, then they will jump. Each ghost jumps differently.
\begin{description}[leftmargin=*]
	\item[Alice (red):] Move to the flower that matches Alice's hex number and the hex that matches the player's flower number.% That is, Alice moves from $(a_f, a_h)$ to $(a_h, p_f)$.
	\item[Bob (yellow):] Move to the flower that matches Bob's hex number and the hex that matches the player's hex number.% That is, Bob moves from $(b_f, b_h)$ to $(b_h, p_h)$.
	\item[Clyde (green):] Move to the flower that matches the player's flower number and the hex that matches Clyde's hex number.% That is, Clyde moves from $(c_f,c_h)$ to $(p_f, c_h)$.
	\item[Daryl (blue):] Move to the flower that matches the player's hex number and the hex that matches Daryl's hex number.% That is, Daryl moves from $(d_f,d_h)$ to $(p_h, d_h)$.
\end{description}
\end{itemize}
\end{document}